Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-13 paper-1/manuscript.tex
Rev F8c and stats to use median, not mean, D

Finally, given the very clear contrast in $\D{A}{i}$ in the sample network, we considered the possibility that, in the context of the full model, STD could also evoke global suppression in the \msc{} sequence, contrary to our stated hypothesis. If so, we should expect to see less $\D{A}{}$ in \dev{} than \msc{}. To confirm this, we analyzed $\Delta \D{A}{}$ across networks and stimuli, and found it to be robustly negative (T = 955, p = 1.23e-12; one-sided Wilcoxon, n = 120), as can be seen in the inset histogram in Figure \ref{fig8}c. Taken together, we cautiously conclude that, while there is clear evidence for greater global suppression in \msc{} than \dev{} in terms of $\D{}{}$, this difference appears to manifest only weakly in activity differences.
% TODO: In hindsight, I'm not sure where this "weakly" claim comes from. Perhaps from Fig7, lower panels? If so, look at the scales in b and f and reconsider. Note also how the next paragraph seems to require a "not weak" conclusion here.

>>>>

Finally, given the very clear contrast in $\D{A}{i}$ in the sample network, we considered the possibility that, in the context of the full model, STD could also evoke global suppression in the \msc{} sequence, contrary to our stated hypothesis. If so, we should expect to see less $\D{A}{}$ in \dev{} than \msc{}. To confirm this, we analyzed $\Delta \D{A}{}$ across networks and stimuli, and found it to be robustly negative (T = 757, p = 2.66e-14; one-sided Wilcoxon, n = 120), as can be seen in the inset histogram in Figure \ref{fig8}c. Taken together, we cautiously conclude that, while there is clear evidence for greater global suppression in \msc{} than \dev{} in terms of $\D{}{}$, this difference appears to manifest only weakly in activity differences.
% TODO: In hindsight, I'm not sure where this "weakly" claim comes from. Perhaps from Fig7, lower panels? If so, look at the scales in b and f and reconsider. Note also how the next paragraph seems to require a "not weak" conclusion here.
